---
title: "Statistical Analyses and Manifests for ATC Experiment E1"
author: "Russell J. Boag"
date: "11 July 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load data, echo=FALSE, include=FALSE}
rm(list=ls())
# setwd("~/russ_model_analyses")
setwd("C:/Users/Russell Boag/Documents/GitHub/DMCATC")
source("dmc/dmc.R")
load_model ("LBA","lbaN_B.R")
source("LSAnova.R")
require("lsr")
require("lme4")
require("car")
pkgs <- c("plyr", "dplyr", "tidyr", "broom", "pander", "xtable")
# install.packages(pkgs) #install
sapply(pkgs, require, character.only = T) #load
# load("~/Modelling/x1/samples/okdats.E1.RData")  # Original data
load("C:/Users/Russell Boag/Documents/GitHub/DMCATC/data/samples/E1.block.B.V_cond.B.V.PMV.samples.RData")  # Samples object
samples.E1 <- E1.block.B.V_cond.B.V.PMV.samples
rm(E1.block.B.V_cond.B.V.PMV.samples)
```

```{r prep data, echo=FALSE, include=FALSE}
# samples.E1[["p17"]]$data[ (samples.E1[["p17"]]$data$S=="pc" | samples.E1[["p17"]]$data$S=="pn"  ) & samples.E1[["p17"]]$data$S=="P" ]

# names(samples.E1) != "p17"
samples.E1 <- samples.E1[names(samples.E1) != "p17"]  # Exclude p17 E1 due to no PM responses

# # # Get data from samples object # # #
#
get.hdata.dmc <- function(hsamples){
  list.wind<-lapply(seq_along(hsamples), function(samples, n, i) cbind(n[[i]], samples[[i]]$data),
                    samples= hsamples, n = names(hsamples))
  out<-do.call(rbind, list.wind)
  names(out)[1] <- "s"
  out
}

#

data.E1 <- get.hdata.dmc(samples.E1)  # Get data from samples object
# head(data.E1)
# save(data.E1, file="data.E1.RData")

# all.equal(datE1[order(datE1$s),], data2)  # Check recovered data matches original data


# # # Add logical S-R match factor 'C' # # #
#
data.E1$C <- rep(0,length(data.E1$RT))
for(i in 1:length(data.E1$RT)){
  if(data.E1$S[i]=="cc" & data.E1$R[i]=="C"){
    data.E1$C[i] <- 1
  } else if(data.E1$S[i]=="nn" & data.E1$R[i]=="N"){
    data.E1$C[i] <- 1
  } else if(data.E1$S[i]=="pc" & data.E1$R[i]=="P"){
    data.E1$C[i] <- 1
  } else if(data.E1$S[i]=="pn" & data.E1$R[i]=="P"){
    data.E1$C[i] <- 1
  }
}
#
```

```{r run GLMER accuracy analyses, echo=FALSE, include=FALSE}

# # # Prep dataframes for analysis # # #
#
setwd("C:/Users/Russell Boag/Documents/GitHub/DMCATC/analysis")

# Conflict Detection Task trials only (no PM)
CDT <- data.E1[!(data.E1$S=="pc" | data.E1$S=="pn"),]
CDT$S <- factor(as.character(CDT$S)); CDT$R <- factor(as.character(CDT$R))
# str(CDT)
# head(CDT)

# PM Task trials only
PMT <- data.E1[(data.E1$S=="pc" | data.E1$S=="pn"),]
PMT$S <- factor(as.character(PMT$S)); PMT$block <- factor(as.character(PMT$block))
# str(PMT)
# head(PMT)
#

# CDT.Acc.glmer.E1 <- glmer(C ~ S*block*cond+(1|s), data=CDT, family=binomial(link="probit"))
# save(CDT.Acc.glmer.E1, file="CDT.Acc.glmer.E1.RData")
load("CDT.Acc.glmer.E1.RData")
CDT.Acc.glm.E1 <- Anova(CDT.Acc.glmer.E1,type="II")
# CDT.Acc.glm.E1
CDT.Acc.TABLE.E1 <- data.frame(CDT.Acc.glm.E1$Chisq, CDT.Acc.glm.E1$Df, CDT.Acc.glm.E1$Pr)
# CDT.Acc.TABLE.E1
CDT.Acc.TABLE.E1$CDT.Acc.glm.E1.Chisq <- round(CDT.Acc.TABLE.E1$CDT.Acc.glm.E1.Chisq, 2)
CDT.Acc.TABLE.E1$CDT.Acc.glm.E1.Pr <- format.pval(CDT.Acc.TABLE.E1$CDT.Acc.glm.E1.Pr, digits=2, eps= 0.001)
CDT.Acc.TABLE.E1$CDT.Acc.glm.E1.Pr <- gsub("0\\.", ".", CDT.Acc.TABLE.E1$CDT.Acc.glm.E1.Pr)
rownames(CDT.Acc.TABLE.E1) <- c("Stimulus","PM Block","Time Pressure",
                                "Stimulus by PM Block","Stimulus by Time Pressure","PM Block by Time Pressure",
                                "Stimulus by PM Block by Time Pressure")
colnames(CDT.Acc.TABLE.E1) <- c("Chi-square","df","p")
# CDT.Acc.TABLE.E1
# write.csv(CDT.Acc.TABLE.E1, file="analysis/CDT.Acc.TABLE.E1.csv")

# PMT.Acc.glmer.E1 <- glmer(C ~ S*cond+(1|s), data=PMT, family=binomial(link="probit"))
# save(PMT.Acc.glmer.E1, file="PMT.Acc.glmer.E1.RData")
load("PMT.Acc.glmer.E1.RData")
PMT.Acc.glm.E1 <- Anova(PMT.Acc.glmer.E1,type="II")
# PMT.Acc.glm.E1
PMT.Acc.TABLE.E1 <- data.frame(PMT.Acc.glm.E1$Chisq, PMT.Acc.glm.E1$Df, PMT.Acc.glm.E1$Pr)
# PMT.Acc.TABLE.E1
PMT.Acc.TABLE.E1$PMT.Acc.glm.E1.Chisq <- round(PMT.Acc.TABLE.E1$PMT.Acc.glm.E1.Chisq, 2)
PMT.Acc.TABLE.E1$PMT.Acc.glm.E1.Pr <- format.pval(PMT.Acc.TABLE.E1$PMT.Acc.glm.E1.Pr, digits=2, eps= 0.001)
PMT.Acc.TABLE.E1$PMT.Acc.glm.E1.Pr <- gsub("0\\.", ".", PMT.Acc.TABLE.E1$PMT.Acc.glm.E1.Pr)
rownames(PMT.Acc.TABLE.E1) <- c("Stimulus","Time Pressure",
                                "Stimulus by Time Pressure")
colnames(PMT.Acc.TABLE.E1) <- c("Chi-square","df","p")
# PMT.Acc.TABLE.E1
# write.csv(PMT.Acc.TABLE.E1, file="analysis/PMT.Acc.TABLE.E1.csv")

setwd("C:/Users/Russell Boag/Documents/GitHub/DMCATC")
```

```{r run LMER RT analyses, echo=FALSE, include=FALSE}
# # # Prep RT dataframes for analysis (keep correct RTs only) # # #
#
setwd("C:/Users/Russell Boag/Documents/GitHub/DMCATC/analysis")

# Conflict Detection Task correct response trials only (no PM)
CDT.RT <- arr2df(tapply(CDT$RT[CDT$C==1],
                         list(s=CDT$s[CDT$C==1], block=CDT$block[CDT$C==1],
                              cond=CDT$cond[CDT$C==1], S=CDT$S[CDT$C==1]), mean))
# head(CDT.RT)
# str(CDT.RT)

# PM Task correct response trials only
PMT.RT <- arr2df(tapply(PMT$RT[PMT$C==1],
                        list(s=PMT$s[PMT$C==1], cond=PMT$cond[PMT$C==1], S=PMT$S[PMT$C==1]), mean))
# head(PMT.RT)
# str(PMT.RT)


# CDTC.RT.lmer.E1 <- lmer(y ~ S*block*cond+(1|s), data=CDT.RT)
# save(CDTC.RT.lmer.E1, file="CDTC.RT.lmer.E1.RData")
load("CDTC.RT.lmer.E1.RData")
CDT.RT.glm.E1 <- Anova(CDTC.RT.lmer.E1,type="II")
# CDT.RT.glm.E1
CDT.RT.TABLE.E1 <- data.frame(CDT.RT.glm.E1$Chisq, CDT.RT.glm.E1$Df, CDT.RT.glm.E1$Pr)
CDT.RT.TABLE.E1$CDT.RT.glm.E1.Chisq <- round(CDT.RT.TABLE.E1$CDT.RT.glm.E1.Chisq, 2)
CDT.RT.TABLE.E1$CDT.RT.glm.E1.Pr <- format.pval(CDT.RT.TABLE.E1$CDT.RT.glm.E1.Pr, digits=2, eps= 0.001)
CDT.RT.TABLE.E1$CDT.RT.glm.E1.Pr <- gsub("0\\.", ".", CDT.RT.TABLE.E1$CDT.RT.glm.E1.Pr)
rownames(CDT.RT.TABLE.E1) <- c("Stimulus","PM Block","Time Pressure",
                               "Stimulus by PM Block","Stimulus by Time Pressure","PM Block by Time Pressure",
                               "Stimulus by PM Block by Time Pressure")
colnames(CDT.RT.TABLE.E1) <- c("Chi-square","df","p")
# CDT.RT.TABLE.E1
# write.csv(CDT.RT.TABLE.E1, file="analysis/CDT.RT.TABLE.E1.csv")

# PMTC.RT.lmer.E1 <- lmer(y ~ S*cond+(1|s), data=PMT.RT)
# save(PMTC.RT.lmer.E1, file="PMTC.RT.lmer.E1.RData")
load("PMTC.RT.lmer.E1.RData")
PMT.RT.glm.E1 <- Anova(PMTC.RT.lmer.E1,type="II")
# PMT.RT.glm.E1
PMT.RT.TABLE.E1 <- data.frame(PMT.RT.glm.E1$Chisq, PMT.RT.glm.E1$Df, PMT.RT.glm.E1$Pr)
PMT.RT.TABLE.E1$PMT.RT.glm.E1.Chisq <- round(PMT.RT.TABLE.E1$PMT.RT.glm.E1.Chisq, 2)
PMT.RT.TABLE.E1$PMT.RT.glm.E1.Pr <- format.pval(PMT.RT.TABLE.E1$PMT.RT.glm.E1.Pr, digits=2, eps= 0.001)
PMT.RT.TABLE.E1$PMT.RT.glm.E1.Pr <- gsub("0\\.", ".", PMT.RT.TABLE.E1$PMT.RT.glm.E1.Pr)
rownames(PMT.RT.TABLE.E1) <- c("Stimulus","Time Pressure",
                                "Stimulus by Time Pressure")
colnames(PMT.RT.TABLE.E1) <- c("Chi-square","df","p")
# PMT.RT.TABLE.E1
# write.csv(PMT.RT.TABLE.E1, file="analysis/PMT.RT.TABLE.E1.csv")

setwd("C:/Users/Russell Boag/Documents/GitHub/DMCATC")

```

```{r calculate manifests and planned contrasts, echo=FALSE, include=FALSE}

setwd("C:/Users/Russell Boag/Documents/GitHub/DMCATC/analysis")
# # # ANOVA analysis: Ongoing Task Accuracy # # #
#
#
# Ongoing Task Accuracy Object
CDT.Acc <- arr2df(tapply(CDT$C,list(s=CDT$s, block=CDT$block, cond=CDT$cond, S=CDT$S),mean))

# str(CDT.Acc)
levels(CDT.Acc$block) <- c("Control","PM")
# levels(CDT.Acc$cond) <- c("LL.LT","LL.HT","HL.LT","HL.HT")
levels(CDT.Acc$S) <- c("Conflict","Nonconflict")
# wsAnova(CDT.Acc)
# Manifests: Ongoing Task Accuracy
CDT.Acc.Means <- mneffects(CDT.Acc,list("S","block","cond",c("S","block"),c("S","cond"),c("block","cond"), digits=3))
CDT.Acc.S <- data.frame(rbind(round(CDT.Acc.Means$S,3), round(se(CDT.Acc, facs=c("S")),3)))
rownames(CDT.Acc.S)<- c("M","SE")
# CDT.Acc.S

CDT.Acc.Block <- data.frame(rbind(round(CDT.Acc.Means$block,3), round(se(CDT.Acc, facs=c("block")),3)))
rownames(CDT.Acc.Block)<- c("M","SE")
# CDT.Acc.Block

CDT.Acc.Cond <- data.frame(rbind(round(CDT.Acc.Means$cond,3), round(se(CDT.Acc, facs=c("cond")),3)))
rownames(CDT.Acc.Cond)<- c("M","SE")
# CDT.Acc.Cond

# round(se(CDT.Acc, facs=c("S","block")),3)
# round(se(CDT.Acc, facs=c("S","cond")),3)
# round(se(CDT.Acc, facs=c("block","cond")),3)
# Split up data object for cond comparisons
CDT.Acc$S <- as.numeric(factor(CDT.Acc$S))
bonf.CDT.Acc <- data.frame()
bonf.CDT.Acc <- tapply(CDT.Acc$y,
                                list(s=CDT.Acc$s,
                                     cond=factor(CDT.Acc$cond)), mean)
# bonf.CDT.Acc
tAB <- t.test (bonf.CDT.Acc[,1], bonf.CDT.Acc[,2], paired=T)
dAB <- cohensD(x=bonf.CDT.Acc[,1], y=bonf.CDT.Acc[,2], method="paired")
tBC <- t.test (bonf.CDT.Acc[,2], bonf.CDT.Acc[,3], paired=T)
dBC <- cohensD(x=bonf.CDT.Acc[,2], y=bonf.CDT.Acc[,3], method="paired")
tAC <- t.test (bonf.CDT.Acc[,1], bonf.CDT.Acc[,3], paired=T)
dAC <- cohensD(x=bonf.CDT.Acc[,1], y=bonf.CDT.Acc[,3], method="paired")

tCD <- t.test (bonf.CDT.Acc[,3], bonf.CDT.Acc[,4], paired=T)
dCD <- cohensD(x=bonf.CDT.Acc[,3], y=bonf.CDT.Acc[,4], method="paired")
tBD <- t.test (bonf.CDT.Acc[,2], bonf.CDT.Acc[,4], paired=T)
dBD <- cohensD(x=bonf.CDT.Acc[,2], y=bonf.CDT.Acc[,4], method="paired")
tAD <- t.test (bonf.CDT.Acc[,1], bonf.CDT.Acc[,4], paired=T)
dAD <- cohensD(x=bonf.CDT.Acc[,1], y=bonf.CDT.Acc[,4], method="paired")

contrasts.CDT.Acc <- data.frame(cbind(rbind(tAB, tBC, tCD),rbind(dAB, dBC, dCD)))
colnames(contrasts.CDT.Acc) <- c("t","df","p","95% CI","Mean Diff","H0","H1","Method","Data","Cohen's d")
contrasts.CDT.Acc <- contrasts.CDT.Acc[, c(1,2,3,5,10)]
row.names(contrasts.CDT.Acc) <- c("A-B","B-C","C-D")
# contrasts.CDT.Acc

# # # ANOVA analysis: Ongoing Task RT # # #
#
#
# Ongoing Task RT Object
CDT.RT <- arr2df(tapply(CDT$RT[CDT$C==1],
                        list(s=CDT$s[CDT$C==1], block=CDT$block[CDT$C==1],
                             cond=CDT$cond[CDT$C==1], S=CDT$S[CDT$C==1]), mean))
# str(CDT.RT)
levels(CDT.RT$block) <- c("Control","PM")
# levels(CDT.RT$cond) <- c("LL.LT","LL.HT","HL.LT","HL.HT")
levels(CDT.RT$S) <- c("Conflict","Nonconflict")
# wsAnova(CDT.RT)
# Manifests: Ongoing Task RT
CDT.RT.Means <- mneffects(CDT.RT,list("S","block","cond",c("S","block"),c("S","cond"), digits=3))

CDT.RT.S <- data.frame(rbind(round(CDT.RT.Means$S,3), round(se(CDT.RT, facs=c("S")),3)))
rownames(CDT.RT.S)<- c("M","SE")
# CDT.RT.S

CDT.RT.Block <- data.frame(rbind(round(CDT.RT.Means$block,3), round(se(CDT.RT, facs=c("block")),3)))
rownames(CDT.RT.Block)<- c("M","SE")
# CDT.RT.Block

CDT.RT.Cond <- data.frame(rbind(round(CDT.RT.Means$cond,3), round(se(CDT.RT, facs=c("cond")),3)))
rownames(CDT.RT.Cond)<- c("M","SE")
# CDT.RT.Cond

round(se(CDT.RT, facs=c("S","cond")),3)
# Split up data object for cond comparisons
CDT.RT$S <- as.numeric(factor(CDT.RT$S))
bonf.CDT.RT <- data.frame()
bonf.CDT.RT <- tapply(CDT.RT$y,
                       list(s=CDT.RT$s,
                            cond=factor(CDT.RT$cond)), mean)
# bonf.CDT.RT
tAB <- t.test (bonf.CDT.RT[,1], bonf.CDT.RT[,2], paired=T)
dAB <- cohensD(x=bonf.CDT.RT[,1], y=bonf.CDT.RT[,2], method="paired")
tBC <- t.test (bonf.CDT.RT[,2], bonf.CDT.RT[,3], paired=T)
dBC <- cohensD(x=bonf.CDT.RT[,2], y=bonf.CDT.RT[,3], method="paired")
tAC <- t.test (bonf.CDT.RT[,1], bonf.CDT.RT[,3], paired=T)
dAC <- cohensD(x=bonf.CDT.RT[,1], y=bonf.CDT.RT[,3], method="paired")

tCD <- t.test (bonf.CDT.RT[,3], bonf.CDT.RT[,4], paired=T)
dCD <- cohensD(x=bonf.CDT.RT[,3], y=bonf.CDT.RT[,4], method="paired")
tBD <- t.test (bonf.CDT.RT[,2], bonf.CDT.RT[,4], paired=T)
dBD <- cohensD(x=bonf.CDT.RT[,2], y=bonf.CDT.RT[,4], method="paired")
tAD <- t.test (bonf.CDT.RT[,1], bonf.CDT.RT[,4], paired=T)
dAD <- cohensD(x=bonf.CDT.RT[,1], y=bonf.CDT.RT[,4], method="paired")

contrasts.CDT.RT <- data.frame(cbind(rbind(tAB, tBC, tCD),rbind(dAB, dBC, dCD)))
colnames(contrasts.CDT.RT) <- c("t","df","p","95% CI","Mean Diff","H0","H1","Method","Data","Cohen's d")
contrasts.CDT.RT <- contrasts.CDT.RT[, c(1,2,3,5,10)]
row.names(contrasts.CDT.RT) <- c("A-B","B-C","C-D")
# contrasts.CDT.RT


# # # ANOVA analysis: PM Accuracy # # #
#
#
# PM Accuracy Object
PMT.Acc <- arr2df(tapply(PMT$C,
                         list(s=PMT$s, cond=PMT$cond, S=PMT$S),mean))
# str(PMT.Acc)
# levels(PMT.Acc$cond) <- c("LL.LT","LL.HT","HL.LT","HL.HT")
levels(PMT.Acc$S) <- c("PM_Conflict","PM_Nonconflict")
# wsAnova(PMT.Acc)
PMT.Acc.Means <- mneffects(PMT.Acc,list("S","cond",c("S","cond"), digits=3))

PMT.Acc.S <- data.frame(rbind(round(PMT.Acc.Means$S,3), round(se(PMT.Acc, facs=c("S")),3)))
rownames(PMT.Acc.S)<- c("M","SE")
# PMT.Acc.S

PMT.Acc.Cond <- data.frame(rbind(round(PMT.Acc.Means$cond,3), round(se(PMT.Acc, facs=c("cond")),3)))
rownames(PMT.Acc.Cond)<- c("M","SE")
# PMT.Acc.Cond

# Split up data object for cond comparisons
PMT.Acc$S <- as.numeric(factor(PMT.Acc$S))
bonf.PMT.Acc <- data.frame()
bonf.PMT.Acc <- tapply(PMT.Acc$y,
                       list(s=PMT.Acc$s,
                            cond=factor(PMT.Acc$cond)), mean)
# bonf.PMT.Acc
tAB <- t.test (bonf.PMT.Acc[,1], bonf.PMT.Acc[,2], paired=T)
dAB <- cohensD(x=bonf.PMT.Acc[,1], y=bonf.PMT.Acc[,2], method="paired")
tBC <- t.test (bonf.PMT.Acc[,2], bonf.PMT.Acc[,3], paired=T)
dBC <- cohensD(x=bonf.PMT.Acc[,2], y=bonf.PMT.Acc[,3], method="paired")
tAC <- t.test (bonf.PMT.Acc[,1], bonf.PMT.Acc[,3], paired=T)
dAC <- cohensD(x=bonf.PMT.Acc[,1], y=bonf.PMT.Acc[,3], method="paired")

tCD <- t.test (bonf.PMT.Acc[,3], bonf.PMT.Acc[,4], paired=T)
dCD <- cohensD(x=bonf.PMT.Acc[,3], y=bonf.PMT.Acc[,4], method="paired")
tBD <- t.test (bonf.PMT.Acc[,2], bonf.PMT.Acc[,4], paired=T)
dBD <- cohensD(x=bonf.PMT.Acc[,2], y=bonf.PMT.Acc[,4], method="paired")
tAD <- t.test (bonf.PMT.Acc[,1], bonf.PMT.Acc[,4], paired=T)
dAD <- cohensD(x=bonf.PMT.Acc[,1], y=bonf.PMT.Acc[,4], method="paired")

contrasts.PMT.Acc <- data.frame(cbind(rbind(tAB, tBC, tCD),rbind(dAB, dBC, dCD)))
colnames(contrasts.PMT.Acc) <- c("t","df","p","95% CI","Mean Diff","H0","H1","Method","Data","Cohen's d")
contrasts.PMT.Acc <- contrasts.PMT.Acc[, c(1,2,3,5,10)]
row.names(contrasts.PMT.Acc) <- c("A-B","B-C","C-D")
# contrasts.PMT.Acc

# # # ANOVA analysis: PM RT # # #
#
#
# PM RT Object
PMT.RT <- arr2df(tapply(PMT$RT[PMT$C==1],
                        list(s=PMT$s[PMT$C==1], cond=PMT$cond[PMT$C==1], S=PMT$S[PMT$C==1]), mean))
# str(PMT.RT)
# levels(PMT.RT$cond) <- c("LL.LT","LL.HT","HL.LT","HL.HT")
levels(PMT.RT$S) <- c("PM_Conflict","PM_Nonconflict")
# wsAnova(PMT.RT)
PMT.RT.Means <- mneffects(PMT.RT,list("S","cond",c("S","cond"), digits=3))

PMT.RT.S <- data.frame(rbind(round(PMT.RT.Means$S,3), round(se2(PMT.RT, facs=c("S")),3)))
rownames(PMT.RT.S)<- c("M","SE")
# PMT.RT.S

PMT.RT.Cond <- data.frame(rbind(round(PMT.RT.Means$cond,3), round(se2(PMT.RT, facs=c("cond")),3)))
rownames(PMT.RT.Cond)<- c("M","SE")
# PMT.RT.Cond

# Split up data object for cond comparisons
PMT.RT$S <- as.numeric(factor(PMT.RT$S))
bonf.PMT.RT <- data.frame()
bonf.PMT.RT <- tapply(PMT.RT$y,
                      list(s=PMT.RT$s,
                           cond=factor(PMT.RT$cond)), mean)
# bonf.PMT.RT
tAB <- t.test (bonf.PMT.RT[,1], bonf.PMT.RT[,2], paired=T)
dAB <- cohensD(x=bonf.PMT.RT[,1], y=bonf.PMT.RT[,2], method="paired")
tBC <- t.test (bonf.PMT.RT[,2], bonf.PMT.RT[,3], paired=T)
dBC <- cohensD(x=bonf.PMT.RT[,2], y=bonf.PMT.RT[,3], method="paired")
tAC <- t.test (bonf.PMT.RT[,1], bonf.PMT.RT[,3], paired=T)
dAC <- cohensD(x=bonf.PMT.RT[,1], y=bonf.PMT.RT[,3], method="paired")

tCD <- t.test (bonf.PMT.RT[,3], bonf.PMT.RT[,4], paired=T)
dCD <- cohensD(x=bonf.PMT.RT[,3], y=bonf.PMT.RT[,4], method="paired")
tBD <- t.test (bonf.PMT.RT[,2], bonf.PMT.RT[,4], paired=T)
dBD <- cohensD(x=bonf.PMT.RT[,2], y=bonf.PMT.RT[,4], method="paired")
tAD <- t.test (bonf.PMT.RT[,1], bonf.PMT.RT[,4], paired=T)
dAD <- cohensD(x=bonf.PMT.RT[,1], y=bonf.PMT.RT[,4], method="paired")

contrasts.PMT.RT <- data.frame(cbind(rbind(tAB, tBC, tCD),rbind(dAB, dBC, dCD)))
colnames(contrasts.PMT.RT) <- c("t","df","p","95% CI","Mean Diff","H0","H1","Method","Data","Cohen's d")
contrasts.PMT.RT <- contrasts.PMT.RT[, c(1,2,3,5,10)]
row.names(contrasts.PMT.RT) <- c("A-B","B-C","C-D")

# # # ANOVA analysis: Ongoing RT for PM versus non-PM Trials # # #
#
#
# Ongoing Task RT Object
# str(data.E1)
# any((data.E1$block=="3" & data.E1$S=="pc" & data.E1$R=="C"))
# any((data.E1$block=="3" & data.E1$S=="pn" & data.E1$R=="N"))

CDT.Reactive <- data.E1[(data.E1$block=="3" & ((data.E1$S=="cc" & data.E1$R=="C") | (data.E1$S=="pc" & data.E1$R=="C") |
                                                   (data.E1$S=="nn" & data.E1$R=="N") | (data.E1$S=="pn" & data.E1$R=="N"))),]
CDT.Reactive$block <- factor(CDT.Reactive$block)
CDT.Reactive$R <- factor(CDT.Reactive$R)
# any((CDT.Reactive$block=="3" & CDT.Reactive$S=="pc" & CDT.Reactive$R=="C"))
# any((CDT.Reactive$block=="3" & CDT.Reactive$S=="pn" & CDT.Reactive$R=="N"))
# any(CDT.Reactive$R=="P")
# any(CDT.Reactive$block=="2")
# any(CDT.Reactive$S=="pc")
# str(CDT.Reactive)
# levels(CDT.Reactive$cond) <- c("LL.LT","LL.HT","HL.LT","HL.HT")
levels(CDT.Reactive$S) <- c("Conflict","Nonconflict","PM_Conflict","PM_Nonconflict")
CDT.Reactive <- arr2df(tapply(CDT.Reactive$RT,
                        list(s=CDT.Reactive$s,
                             cond=CDT.Reactive$cond, S=CDT.Reactive$S), mean))
# str(CDT.Reactive)
# CDT.Reactive.lmer.E1 <- lmer(y ~ S*cond+(1|s), data=CDT.Reactive)
# save(CDT.Reactive.lmer.E1, file="CDT.Reactive.lmer.E1.RData")
load("CDT.Reactive.lmer.E1.RData")
CDT.Reactive.glm.E1 <- Anova(CDT.Reactive.lmer.E1,type="II")
# CDT.Reactive.glm.E1
CDT.Reactive.TABLE.E1 <- data.frame(CDT.Reactive.glm.E1$Chisq, CDT.Reactive.glm.E1$Df, CDT.Reactive.glm.E1$Pr)
CDT.Reactive.TABLE.E1$CDT.Reactive.glm.E1.Chisq <- round(CDT.Reactive.TABLE.E1$CDT.Reactive.glm.E1.Chisq, 2)
CDT.Reactive.TABLE.E1$CDT.Reactive.glm.E1.Pr <- format.pval(CDT.Reactive.TABLE.E1$CDT.Reactive.glm.E1.Pr, digits=2, eps= 0.001)
CDT.Reactive.TABLE.E1$CDT.Reactive.glm.E1.Pr <- gsub("0\\.", ".", CDT.Reactive.TABLE.E1$CDT.Reactive.glm.E1.Pr)
rownames(CDT.Reactive.TABLE.E1) <- c("Stimulus","Time Pressure","Stimulus by Time Pressure")
colnames(CDT.Reactive.TABLE.E1) <- c("Chi-square","df","p")
# wsAnova(CDT.Reactive)
CDT.Reactive.Means <- mneffects(CDT.Reactive,list("S","cond", digits=3))

CDT.Reactive.S <- data.frame(rbind(round(CDT.Reactive.Means$S,3), round(se2(CDT.Reactive, facs=c("S")),3)))
rownames(CDT.Reactive.S)<- c("M","SE")
# CDT.Reactive.S

CDT.Reactive.Cond <- data.frame(rbind(round(CDT.Reactive.Means$cond,3), round(se2(CDT.Reactive, facs=c("cond")),3)))
rownames(CDT.Reactive.Cond)<- c("M","SE")
# CDT.Reactive.Cond

# Split up data object for S comparisons
CDT.Reactive$S <- as.numeric(factor(CDT.Reactive$S))
bonf.CDT.Reactive <- data.frame()
bonf.CDT.Reactive <- tapply(CDT.Reactive$y,
                      list(s=CDT.Reactive$s,
                           S=factor(CDT.Reactive$S)), mean)
# bonf.CDT.Reactive
tccpc <- t.test (bonf.CDT.Reactive[,1], bonf.CDT.Reactive[,3], paired=T)
dccpc <- cohensD(x=bonf.CDT.Reactive[,1], y=bonf.CDT.Reactive[,3], method="paired")
tnnpn <- t.test (bonf.CDT.Reactive[,2], bonf.CDT.Reactive[,4], paired=T)
dnnpn <- cohensD(x=bonf.CDT.Reactive[,2], y=bonf.CDT.Reactive[,4], method="paired")

contrasts.Reactive <- data.frame(cbind(rbind(tccpc, tnnpn),rbind(dccpc, dnnpn)))
colnames(contrasts.Reactive) <- c("t","df","p","95% CI","Mean Diff","H0","H1","Method","Data","Cohen's d")
contrasts.Reactive <- contrasts.Reactive[, c(1,2,3,5,10)]
row.names(contrasts.Reactive) <- c("CR minus CR-to-PMC","NR minus NR-to-PMN")
# contrasts.Reactive

setwd("C:/Users/Russell Boag/Documents/GitHub/DMCATC")

```


## Ongoing Task Accuracy GLMER

```{r CDT Accuracy GLMER, echo=FALSE}

panderOptions("digits", 4)

lmer <- CDT.Acc.TABLE.E1
means1 <- CDT.Acc.S
means2 <- CDT.Acc.Block
means3 <- CDT.Acc.Cond
contrasts <- contrasts.CDT.Acc

pander(lmer)
pander(means1)
pander(means2)
pander(means3)
pander(contrasts)
xtable(lmer)

write.csv(lmer, file="analysis/CDT.Acc.TABLE.E1.csv")
write.csv(means1, file="analysis/CDT.Acc.S.E1.csv")
write.csv(means2, file="analysis/CDT.Acc.Block.E1.csv")
write.csv(means3, file="analysis/CDT.Acc.Cond.E1.csv")
# write.csv(contrasts, file="analysis/CDT.Acc.Contrasts.E1.csv")

```

## Ongoing Task RT LMER

```{r CDT RT LMER, echo=FALSE}

panderOptions("digits", 4)

lmer <- CDT.RT.TABLE.E1
means1 <- CDT.RT.S
means2 <- CDT.RT.Block
means3 <- CDT.RT.Cond
contrasts <- contrasts.CDT.RT

pander(lmer)
pander(means1)
pander(means2)
pander(means3)
pander(contrasts)
xtable(lmer)

write.csv(lmer, file="analysis/CDT.RT.TABLE.E1.csv")
write.csv(means1, file="analysis/CDT.RT.S.E1.csv")
write.csv(means2, file="analysis/CDT.RT.Block.E1.csv")
write.csv(means3, file="analysis/CDT.RT.Cond.E1.csv")
# write.csv(contrasts, file="analysis/CDT.RT.Contrasts.E1.csv")

```

## PM Accuracy GLMER

```{r PMT Accuracy GLMER, echo=FALSE}

panderOptions("digits", 4)

lmer <- PMT.Acc.TABLE.E1
means1 <- PMT.Acc.S
means2 <- PMT.Acc.Cond
contrasts <- contrasts.PMT.Acc

pander(lmer)
pander(means1)
pander(means2)
pander(contrasts)
xtable(lmer)

write.csv(lmer, file="analysis/PMT.Acc.TABLE.E1.csv")
write.csv(means1, file="analysis/PMT.Acc.S.E1.csv")
write.csv(means2, file="analysis/PMT.Acc.Cond.E1.csv")
# write.csv(contrasts, file="analysis/PMT.Acc.Contrasts.E1.csv")

```

## PM RT LMER

```{r PMT RT LMER, echo=FALSE}

panderOptions("digits", 4)

lmer <- PMT.RT.TABLE.E1
means1 <- PMT.RT.S
means2 <- PMT.RT.Cond
contrasts <- contrasts.PMT.RT

pander(lmer)
pander(means1)
pander(means2)
pander(contrasts)
xtable(lmer)

write.csv(lmer, file="analysis/PMT.RT.TABLE.E1.csv")
write.csv(means1, file="analysis/PMT.RT.S.E1.csv")
write.csv(means2, file="analysis/PMT.RT.Cond.E1.csv")
# write.csv(contrasts, file="analysis/PMT.RT.Contrasts.E1.csv")

```

## Reactive Control RT Check LMER

Check that congruent ongoing task responses to PM stimuli (i.e., conflict responses to PM conflicts) are faster than correct ongoing task responses to non-PM stimuli (although this will be partly due to statistical facilitation from the fast PM accumulator on PM trials filtering out ongoing task responses).

```{r Reactive Control RT Check, echo=FALSE}

panderOptions("digits", 4)

lmer <- CDT.Reactive.TABLE.E1
means1 <- CDT.Reactive.S
contrasts <- contrasts.Reactive

pander(lmer)
pander(means1)
pander(contrasts)
xtable(lmer)

write.csv(lmer, file="analysis/CDT.Reactive.TABLE.E1.csv")
write.csv(means1, file="analysis/CDT.Reactive.S.E1.csv")
# write.csv(contrasts, file="analysis/CDT.Reactive.Contrasts.E1.csv")

```
